\section{Tools we used}\label{sec:tools}
% section tools
The implementation of the project involved working with a diverse set of tools and technologies. They are outlined in this section.

\textbf{Lift Web Framework}
The Lift Web Framework is a highly secure, reliable framework for building interactive web applications for building Scala web applications. Lift applications are packaged as WAR files and can be deployed on any Servlet engine e.g., Tomcat 5.5, Jetty 6.0.

\textbf{Apache Lucene}
Apache Lucene is a high-performance text search engine written entirely in Java, it is part of Apache Software Foundation. Lucene can index and search any data that can be represented in textual format. 

\textbf{AJAX}
AJAX stands for Asynchronous JavaScript And XML. It is widely used to create interactive, dynamic web applications. 

\textbf{JUnit}
JUnit is a unit testing framework for the Java programming language. 

\textbf{Scala Specs}
Specs is a testing framework for Scala can be integrated with JUnit. Specs allows writing unit 
tests using simple intuite text format

\textbf{JMock}
JMock is a library that supports test-driven development of Java code with mock objects. Mock objects aim for testing the interactions between the objects in an applicatio. The JMock library makes it quick and easy to define mock objects; allows for specifying precisely the interactions between the objects. Moreover, it allows specifying what kind of allowed operations we put to the mock object during the tests.

\textbf{SBT (Simple Build Tool)}
For building Colladoc project we used SBT, an open-source project written in Java. It helped us for compiling, building, running test, as well aspackaging Colladoc project. 

\textbf{Selenium IDE}
As Colladoc Smart Search should have a nice-looking user interface, we agreed on utilizing Selenium for conducting UI integration testing. Selenium provides a record/playback tool for authoring tests without any requirements on learning a test scripting language. Moreover, with the ability to build a specific domain specific language (DSL) Selenium provides a test suit to write tests in a number of popular programming languages, including C$\#$, Java, Groovy, Perl, PHP, Python and Ruby. For our project, we also integrated Selenium IDE, a complete Integrated Development Environment (IDE) for Selenium tests. It is implemented a Firefox extension, and allows recording, editing, and debugging tests.

\textbf{YourKit Java Pro}
For measuring Colladoc Smart Search we chose to use YourKit Pro profiler, a tool dedicated for both development and production stages. The most apparent advantage of this tool is that it can be easily integrated at any  platforms, including Windows, Linux, Solaris SPARC/Intel, and Mac OS X. It has analysis capabilities such as CPU and memory hot spots with devoted views; unique snapshot comparison; memory leak detection; memory distribution reports; measuring of shallow and retained sizes of objects; reporting utility.